---
title: "analysis second round of imaging"
output:
  html_document:
    df_print: paged
---

```{r setup}
library(tidyverse)
library(here)
library(heatmaply)
library(pheatmap)
library(RColorBrewer)
```

First, we load the data. To produce the small tidy table, run the load and process data script in Olaf. The data is aprox. 8 Gb and can't be loaded into memory in my laptop at least.

```{r}
# # k = 1
# j = 1
# todo = list()
# columns_i_like <- c(4,7,36,39,62,63)
# for(i in round(seq(1,4098628, length.out = 1000),0))
# {
#   
#   todo[[k]] <- read.csv(here('second_round_imaging','small_tidy_results.csv'), nrow = 10000, skip =i, header = FALSE)[, columns_i_like]
#   print(i)
#   k = k+1
# }

gene_ids <- read_tsv('../gene_IDs_names.tsv', skip = 1, col_names = c('Systematic','name','extra_names'))

gene_ids[is.na(gene_ids$name),]$name <- gene_ids[is.na(gene_ids$name),]$Systematic

screen_data <- read_delim(here('second_round_imaging','extract_tidy.txt'), delim = ' ')

ggplot(screen_data, aes(AreaShape_Solidity)) +
  geom_histogram()

sum_data <- screen_data %>%
  unite(new_id, c('Well','Metadata_Plate_Name','Systematic'), remove = F) %>%
  filter(AreaShape_Solidity > 0.8 & Time <13) %>%
  left_join(gene_ids, by = c('Systematic')) %>%
  group_by(Systematic, Time, name) %>%
  summarise(mean_size = median(AreaShape_Area)) %>%
  spread(key = Time, value = mean_size) %>%
  write_csv(here('second_round_imaging','median_data.csv'))

sum_data[is.na(sum_data$name),]$name <- 'wt'

ord_sum_data <- sum_data[order(sum_data$`12`, decreasing = T),]

heatmap_data <- pheatmap(ord_sum_data[,-1:-2], cluster_rows = F, labels_row = ord_sum_data$name, color = Purples(10), clustering_method = 'ward.D2',
                         cluster_cols = F)

cl <- data.frame(cl  = cutree(heatmap_data$tree_row, k = 6), ids = sum_data$Systematic) %>%
  write_csv('../second_round_imaging/clusters.csv')
```

Analyse the clusters from the heatmap using clusterprofiler

```{r}
library(clusterProfiler)

cut_tree <- cutree(heatmap_data$tree_row, k = 4)

clusters <- tibble(ID = sum_data$Systematic, cl = cut_tree) %>%
  write_csv(here('second_round_imaging','clusters_Area.csv'))

#ck <- compareCluster(data = clusters, ID ~ cl, fun = 'enrichKEGG', org = 'spo')
```
Create 2D density plot with the summary data, using the real time instead of the time points that come in the image name
```{r}
sum_data_tidy <- screen_data %>%
  group_by(Systematic, Time) %>%
  summarise(mean_size = median(AreaShape_Area), mean_TIME = mean(TIME))


ggplot(sum_data_tidy, aes(x = mean_TIME, y = Systematic, colour = mean_size)) +
  geom_tile()
```

Check wild type data
```{r}
only_wt <- screen_data %>%
  filter(AreaShape_Solidity > 0.9) %>%
  group_by(Time, Metadata_Plate_Name, Systematic) %>%
  summarise(median_area = median(AreaShape_Area), sd_area = sd(AreaShape_Area), mean_area = mean(AreaShape_Area))


only_wt <- screen_data %>%
  filter(Systematic == 'wt' & Time == 11) 

ggplot(only_wt, aes( x = AreaShape_Area, group = Systematic, colour = Well, fill = Well)) +
  facet_grid(~ Metadata_Plate_Name*Well)+
  geom_histogram(alpha = 0.75) +
  scale_x_continuous(limits = c(0, 3000))


ggplot(filter(screen_data, AreaShape_Solidity > 0.9), aes(x = TIME, y = AreaShape_Area, group = Systematic)) +
  facet_grid(~ Metadata_Plate_Name)+
  geom_smooth() +
  geom_smooth(data = filter(only_wt, Systematic == 'wt'),aes( colour = 'red'))
```


```{r}
tp0 <- screen_data %>%
  filter(Time == 0 & AreaShape_Solidity > 0.9) %>%
  group_by(Time, Metadata_Plate_Name, Systematic) %>%
  summarise(median_area = median(AreaShape_Area, na.rm = T), sd_area = sd(AreaShape_Area), mean_area = mean(AreaShape_Area, na.rm = T))

max_increase <- screen_data %>%
  filter(AreaShape_Solidity > 0.9) %>%
  group_by(Metadata_Plate_Name, Systematic) %>%
  summarise(median_area = median(AreaShape_Area,na.rm = T), sd_area = sd(AreaShape_Area), mean_area = mean(AreaShape_Area, na.rm = T), max_area = max(AreaShape_Area)) %>%
  left_join(tp0, by = c('Metadata_Plate_Name', 'Systematic'), suffix = c('.tp15','.tp0')) %>%
  mutate(size_increase = max_area/median_area.tp0)

tp_11 <- screen_data %>%
  filter(Time == 11 & AreaShape_Solidity > 0.8)

hits <- read_csv('../live_cell_imaging_cp/hits_i_guess.csv') %>%
  mutate(size_primary_1 = case_when(mean_area_rep1 > 600 ~ 'big',
                             mean_area_rep1 < 600  ~ 'small'),
         size_primary_2 = case_when(mean_area_rep2 > 600 ~ 'big',
                             mean_area_rep2 < 600  ~ 'small'))

ggplot(hits, aes( x= mean_area_rep1, y = mean_area_rep2)) +
  geom_point() 

tp_11_annot <- tp_11 %>%
  left_join(hits, by = c('Systematic' = 'Systematic ID')) 




ggplot(tp_11_annot, aes(x = reorder(Systematic, AreaShape_Area, FUN = median), y = AreaShape_Area, colour = size_r)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

tp_11_median <- tp_11 %>%
  group_by(Systematic) %>%
  summarise(mean_area = mean(AreaShape_Area)) %>%
  mutate(size_secondary = case_when(mean_area > 347 ~ 'big',
                                    TRUE ~ 'small'))

product_description <- read_tsv('../gene_IDs_names_products.tsv', col_names = c('ID',
                                                                                'PomBaseID',
                                                                                'name',
                                                                                'chromosome',
                                                                                'desc',
                                                                                'UniProt',
                                                                                'coding',
                                                                                'alt_name')) %>%
  select(ID, desc)

all_data <- inner_join(hits, tp_11_median, by = c('Systematic ID' = 'Systematic')) %>%
  inner_join(product_description, by = c('Systematic ID' = 'ID')) %>%
  select(size_primary_1, size_primary_2, size_secondary, `Systematic ID`, desc) %>%
  write_csv('../second_round_imaging/comparison_table.csv')
```

```{r}
cell_areas_1 <- read_csv('../output_rep1/cell_areas.csv')
cell_areas_2 <- read_csv('../output_rep2/areas_rep2.csv')

wt_live_imaging <- tp_11 %>%
  filter(Systematic == 'wt')
for(id in unique(tp_11$Systematic))
{
  primary_1 <- filter(cell_areas_1, Metadata_Plate_Name == id) %>%
    select(`Systematic ID`) %>%
    add_column(screen_type = 'primary_1') %>%
    rename(AreaShape_Area = `Systematic ID`)
  
  primary_2 <- filter(cell_areas_2, `Systematic ID` == id) %>%
    select(AreaShape_Area) %>%
    add_column(screen_type = 'primary_2')
  
  secondary <- filter(tp_11, Systematic == id) %>%
    select(AreaShape_Area) %>%
    add_column(screen_type = 'secondary')
  
  together <- bind_rows(primary_1, primary_2, secondary)
  
  ggplot(together, aes(AreaShape_Area, fill = screen_type)) +
    geom_histogram(alpha = 0.75, bins = 50) +
    geom_histogram(data = wt_live_imaging, aes(AreaShape_Area), alpha = 0.5, inherit.aes = F, bins = 50) +
    facet_wrap(~Metadata_Plate_Name*Well) +
    ggtitle(id) +
    scale_x_log10()
  
  ggsave(paste0('../histogram_replicates/',id,'.jpg'))
}
```


```{r}
sum_1 <- read_csv('../output_rep1/summary_rep1_pval_0.15.csv')
sum_2 <- read_csv('../output_rep2/statistics_rep2_pvalue_0.15.csv')

```
